### 2008-10-22 trunk/Latex/H2Preview/H2PrevConcs.tex
My edits. Change to abstract to reflect new objectives and minor corrections to DJNL's changes.

\label{sec:Conclusions}
Preview control has been studied for at least four decades and a large number of theoretical results can be found in the control and mechanical engineering technical literature. In many cases the theoretical developments on discrete-time $\htwo$/LQG were driven by applications problems. Contemporary applications include for example active automotive suspension control \cite{Roh_1999_Stoc_Opt_Prev,Marzbanrad_2004_SuspPrev}, helicopter flight control \cite{Paulino_2006_PreviewRotorcraftAffine}, 
and driver steering control \cite{Cole_2006_PredictiveAndPreviewSteeringControl}.
Other applications examples, which are also related to vehicle dynamics problems, can be found in the first author's thesis; visit \url{http://code.google.com/p/preview-control-toolbox/}. A MATLAB Preview Control toolbox implementation of the presented algorithms together with their $\hinf$ counterpart can also be obtained this site.

In the authors' opinion the strong influence of applications problems has produced a body of theory that is example-specific and consequently somewhat restricted in terms of its scope and generality. To the best of our knowledge a complete set of tools for synthesising $\htwo$ preview controllers that solve broad range of realistic design problems is unavailable in the open literature. The provision of these tools is the central purpose of the work presented here. We present a general preview problem that captures most of the results in the contemporary literature, as well as offering a solution framework for more complex preview problems such as the preview tracking with integral action problem illustrated in Figure \ref{fig:TrackSysIntegDesign}.

>>>>

\label{sec:Conclusions}
Preview control has been studied for at least four decades and a large number of theoretical results can be found in the control and mechanical engineering technical literature. In many cases the theoretical developments on discrete-time $\htwo$/LQG were driven by applications problems. Contemporary applications include for example active automotive suspension control \cite{Roh_1999_Stoc_Opt_Prev,Marzbanrad_2004_SuspPrev}, helicopter flight control \cite{Paulino_2006_PreviewRotorcraftAffine}, 
and driver steering control \cite{Cole_2006_PredictiveAndPreviewSteeringControl}.
Other applications examples, which are also related to vehicle dynamics problems, can be found in the first author's thesis; visit \url{http://code.google.com/p/preview-control-toolbox/}. A MATLAB Preview Control toolbox implementing the presented algorithms, together with their $\hinf$ counterpart, can also be obtained from this site.

In the authors' opinion the strong influence of applications problems has produced a body of theory that is example-specific and consequently somewhat restricted in terms of its scope and generality. To the best of our knowledge a complete set of tools for synthesising $\htwo$ preview controllers that solve a broad range of realistic design problems is unavailable in the open literature. The provision of these tools is the central purpose of the work presented here. We present a general preview problem that captures most of the results in the contemporary literature, as well as offering a solution framework for more complex preview problems such as the preview tracking with integral action problem illustrated in Figure \ref{fig:TrackSysIntegDesign}.
